Approximation: Greedy and Local Search

### 2024-06-24 presentation/presentation.tex
finished the draft

\usepackage{xcolor}

@@

>>>>

\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{marvosym}

@@

\begin{frame}{Scheduling on Identical Paralle Machines}
    \textbf{Problem Statement: } Given $n$ jobs to be processed on $k$ 
    machines, How can we schedule them such that they will finish as early as possible. \brk 
    \begin{itemize}
        \item What if there is not deadline?
        \item How do we define earlieness/lateness?
    \end{itemize}
\end{frame}

\begin{frame}{Scheduling on Identical Paralle Machines - Formal Definition}
    More machines $\implies$ more complexity \brk 
    So the problem is \textbf{NP-hard} even if \brk 
    \ \ \ \ we don't consider \color{red} release time \color{black} and \color{red} deadlines \color{black}
\end{frame}

\begin{frame}{Scheduling on Identical Paralle Machines - Formal Definition}
    \textbf{Input:} $n$ jobs with processing time $p_j$ and $k$ machines \brk 
    \textbf{Output:} A schedule that minimizes 
    \begin{align*}
        \max_{j \in [n]} C_j 
    \end{align*}
    where $C_j$ is the completion time of job $j$.
\end{frame}

\begin{frame}{Algorithm - Local Search}
    \textbf{Recap:} Local search 
    \begin{itemize}
        \item<1-3> starts with a valid solution 
        \item<2-3> searches greedily until 
        \item<3> no better strategy can be made 
        \item<4> How do we find a valid solution?
        \item<4> How to make greedy strategy?
    \end{itemize}
\end{frame}

\begin{frame}{Algorithm - Local Search}
    \textbf{Recap:} Local search 
    \begin{itemize}
        \item<1-> How do we find a valid solution?
        \item<2-> \color{red} Finish all jobs in one machine. \color{black}
        \item<1-> How to make greedy strategy?
        \item<3-> \color{red} Separate those jobs to other machines. \color{black}
    \end{itemize}
\end{frame}

\begin{frame}{Local Search - Seperation of Jobs}
    \begin{itemize}
        \item Pick the last job $j$ at the machine $M$ with the latest running time
        \item Let $t$ be the processing time of all other jobs on $M$
        \item Find another machine $M'$ such that $t' < t$ is minimized
        \item Add $j$ to $M'$
    \end{itemize}
    \pause 
    But, can we go into \color{red} LOOPs \color{black}?
\end{frame}

\begin{frame}{Local Search - Analysis}
    We show that a job is only assigned \textbf{once} in our local search algorithm. \brk 
    \textbf{Suppose} that a job $j$ on machine $M$ is assigned for a \textbf{second} time. \brk \pause
    $\implies$ machine $M$ has the latest running time \brk \pause
    $\implies$ there is another machine $M'$ such that $t' < t$ \brk \pause 
    \textbf{BUT}: by our strategy $t$ has to be minimal when $j$ was assigned at an earlier step. \brk \pause 
    \ \ \ \ We denote completion time on $M'$ at this step as $t'_0$, it holds 
    \begin{align*}
        t' \geq t'_0 \geq t \ \mbox{\Lightning}
    \end{align*}  
\end{frame}

\begin{frame}{Local Search - Analysis}
    What about the approximation ratio? \brk \pause 
    \begin{itemize}
        \item Completion time on each machine should be close to mean: $$\dfrac{\sum_{j \in [n]}p_j}{n}$$
        \item It's also the case for the optimal solution, and $$|Opt^*| \geq \dfrac{\sum_{j \in [n]}p_j}{k}$$
        \item We show $$|Opt| \leq \dfrac{2\sum_{j \in [n]}p_j}{k} \leq 2|Opt^*|$$
    \end{itemize}
\end{frame}

\begin{frame}{Local Search - Analysis}
    We show $$|Opt| \leq \dfrac{2\sum_{j \in [n]}p_j}{k}$$ 
    \begin{itemize}
        \item Consider the machine $M$ with the longest completion time 
        \item Job $j$ that completes last with processing time $p_j$ 
        \item All other jobs completes at $t$.
    \end{itemize}
    We have $$|Opt| = t + p_j$$ and we may witness 
    \begin{align*}
        t &\leq  \dfrac{\sum_{j \in [n]}p_j}{k} \\ 
        p_j &\leq  \dfrac{\sum_{j \in [n]}p_j}{k}
    \end{align*}
\end{frame}

\begin{frame}{Algorithm - Greedy and More}
    \begin{itemize}
        \item There exists greedy algorithm that solves problem with $\alpha = 2, \dfrac{4}{3}$
        \item With rounding and DP, the problem can be approximated with $\alpha = 1 +\epsilon$ for any $\epsilon > 0$
    \end{itemize}
\end{frame}
